Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-02 ms.tex
added figure showing best-fit f1 in Lambert projection, to highlight north Galactic pole

% should really change labels to have **script** I to be consistent with the
% notation used in the text

@@

We adopt the thermal dust emission model of FDS99, which consists of two 
populations of dust grains emitting as MBBs, but with different temperatures 
and different emissivity power law indices $\beta$. The shape of this spectrum 
is given by:

@@

With $\nu_0$ = 3000 GHz, $f_{1}$ = 0.0363, $\beta_1$ = 1.67, $\beta_2$ = 2.70, 
and $q_1/q_2$ = 13.0. For the parameters thus far specified, the two dust 
temperatures are further related by:

@@

@@

>>>>

@@

We adopt the thermal dust emission model of FDS99, which consists of two 
populations of dust grains emitting as MBBs, each with distinct 
emission/absorption characteristics. Importantly, the emissivity power 
law indices $\beta$ of the two species differ. The shape of this spectrum is 
given by:

@@

With $f_{1}$ = 0.0363, $\beta_1$ = 1.67, $\beta_2$ = 2.70, and $q_1/q_2$ = 
13.0. $\nu_0$ is chosen to be 3000 GHz. For the parameters thus far specified, 
the two dust temperatures are further related by:

@@

% more important than the details of the above equation is the notion
% that, for any set of f1, q1/q2, beta1, beta2, the relationship between
% T1 and T2 is a simple power law

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_lambert.eps, width=3.3in}
\caption{\label{fig:f1lambert} The results of our low-resolution fit with $f_1$
allowed to vary, shown in Lambert projection to highlight the salient features 
near the north Galactic pole.}
\end{center}
\end{figure}
